---
title: "Case Study 1"
author: "Nicolas Bschor 12132344"
date: '2022-03-29'
output: pdf_document
---

First we have to define the libraries we will use in the project.

```{r setup}
library(microbenchmark)
```

# Ratio of Fibonacci numbers

## 1

In this exercise we write the Ratio of Fibonacci numbers given as $r_n = F_{n+1} / F_n$ with $F_n$ as the $n$th Fibonacci number. First with a ``for`` loop: 


```{r}
ratio_fibonacci_for <- function(n) {
  f0 <- 0
  f1 <- 1
  r_f = 1:n
  
  if(n == 0) {
    return(0)  
  }
  
  for(i in 1:n) {
    f_new <- f0 + f1
    f0 <- f1
    f1 <- f_new
    
    r_f[i]<- f1/ f0
  }
  
  return(r_f)
}

```

and afterwards with a ``while`` loop: 

```{r}
ratio_fibonacci_while <- function(n) {
  i <- 0
  f0 <- 0
  f1 <- 1
  r_f = 1:n
  
  if(n == 0) {
    return(0)  
  }
  
  while(i < n) {
    i <- i+1
    f_new <- f0 + f1
    f0 <- f1
    f1 <- f_new
    
    r_f[i]<- f1/ f0
  }
  
  return(r_f)
}
```

We can check if both functions create the same output. 

```{r}
set.seed(420)
functions_equal <- TRUE

for(rand_int in sample.int(n = 100, size = 10)) {
  n_rf_for <- ratio_fibonacci_for(rand_int)
  n_rf_while <- ratio_fibonacci_while(rand_int)
  
  if(!all.equal(n_rf_for, n_rf_while)) {
    functions_equal <- FALSE
    break
  }
}

if(functions_equal) {
  print("Functions produce the same output")
} else {
  print("Functions don't produce the same output")
}
  
```

## 2

With the ``microbenchmark`` command we can compare the two functions with $100$ and 
$1000$ as input values.

```{r}
microbenchmark(ratio_fibonacci_for(100), ratio_fibonacci_for(1000), 
               ratio_fibonacci_while(100), ratio_fibonacci_while(1000))
```
Given the results, we can see that the function with a ``for`` loop is faster in 
general with 100 or 1000 values.  


## 3 

```{r}
rf <- ratio_fibonacci_for(100)
plot(rf, type="l", main="Ratio of Fibonacci numbers", xlab="x", ylab="y")
```

In the plot we can see, that the ratio fibonacci series converge to `r rf[100]`.


# The golden ratio

```{r}
phi <- (sqrt(5) + 1) / 2
x <- 1:1000
phi_power = phi^(x+1)
phi_sum = phi^(x) + phi^(x-1)

res_equal_op <- phi_sum == phi_power
length(res_equal_op[res_equal_op==TRUE]) == length(res_equal_op)

res_all_equal <- all.equal(phi_power, phi_sum)
res_all_equal
```
With the ``==`` operator we can see that the two arrays doesn't are the same. 
So there are some differences, but these are very small ($\Delta \approx 10^-16$). 
This is probably do to the numeric handling of the numbers. 
The ``all.equal`` function tested the two arrays if they are 'near equality', 
so the small rounding differences are not taken into account.
Using this function, we can see that $\Phi^{n+1} = \Phi^n + \Phi^{n-1}$.

# Game of craps

```{r}
roll_dice <- function() {return( sum(sample(1:6, 2)) )}

game_of_craps <- function() {
  
  res_1 <- roll_dice()
  
  if(res_1 == 7 || res_1 == 11) {
    return(TRUE)
  }
  
  while(TRUE) {
    res_n <- roll_dice()
    
    if(res_n == res_1)
      return(TRUE)
    else if(res_n == 7 || res_n == 11) 
      return(FALSE)
  }
} 
```

We created the function ``roll_dice`` which returns the sum of two random numbers ranging from $1$ to $6$.
In the ``game_of_craps`` function the main game is simulated. It returns ``TRUE`` if the game is won, 
``FALSE`` when the player lost the game. 

First the function ``roll_dice`` is called and the result is stored in the ``res_1`` variable. 
If the result is $7$ or $11$ the player wins the game, if not the second part 
of the games starts in a ``while`` loop. 
It starts by roll the dice again and the result is stored in the variable ``res_n``. 
Now the result of the first roll_dice and the one in the while loop are compared. 
If they are equal the program stops with ``TRUE``. 
If the new result is $7$ or $11$ the program terminates with ``FALSE``. 
In every other case the program starts again.


# Readable and efficient code

## Function foobar0

First we can define the 'bad' function foobar0.

```{r}
foobar0 <- function(x, z) {
  if (sum(x >= .001) < 1) {
    stop("step 1 requires 1 observation(s) with value >= .001")
  }
  fit <- lm(x ~ z)
  r <- fit$residuals
  x <- sin(r) + .01
  
  if (sum(x >= .002) < 2) {
    stop("step 2 requires 2 observation(s) with value >= .002")
  }
  fit <- lm(x ~ z)
  r <- fit$residuals
  x <- 2 * sin(r) + .02
  
  if (sum(x >= .003) < 3) {
    stop("step 3 requires 3 observation(s) with value >= .003")
  }
  fit <- lm(x ~ z)
  r <- fit$residuals
  x <- 3 * sin(r) + .03
  
  if (sum(x >= .004) < 4) {
    stop("step 4 requires 4 observation(s) with value >= .004")
  }
  fit <- lm(x ~ z)
  r <- fit$residuals
  x <- 4 * sin(r) + .04
  
  return(x)
}
```

## Function improve

Now we can improve the function by reducing repetitive and combine different parts in functions. 

```{r}
transform_input <- function(x, z, n) {
  fit <- lm(x ~ z)
  r <- fit$residuals
  return(n * sin(r) + (.01 * n))
}

check_input <- function(x, n) {
  if (sum(x >= (n*.001)) < n) {
    stop(paste("step", n, "requires", n, 
               "observation(s) with value >=", (n * .001), sep = " "))
  }
}

foobar <- function(x, z) {
  for(i in 1:4) {
    check_input(x, i)
    x <- transform_input(x, z, i)
  }

  return(x)
}
```

## Validation 

To check the new function we can use the following code.

```{r}
for(i in 1:00) {
  set.seed(1)
  x <- rnorm(100)
  z <- rnorm(100)
  
  if(!all.equal(foobar0(x,z), foobar(x, z))) {
    stop("Functions produce different output")
  }
}

print("Functions produce equal output")
```